Technical Dimensions of Programming Systems

### 2022-09-29 prog-2022/changelog.tex
Penultimate pre-submission stuff

Section~5 has been clarified as an evaluation of the framework by means
of the two example usages. We've included a summary table for the
dimensional analysis of Dark in section~5.1 and annotated the screenshot
for convenience. We appreciate the reviewer's desire for examples of the
specific interactions, but we thought it'd be pointless to write down
something already explained in one of Dark's tutorial videos, so we
cited the latter instead.

@@

Our statement about ``cool/interesting'' was entirely from experience,
so we relaxed it to something we could more easily support with
references. These can be seen in a footnote with our remarks linking
them to the point we're trying to make. Elsewhere we have addressed this
by deleting the claim (e.g.~for ``holistic view'') or adding references,
for example to the various example systems like Java and Jupyter. We're
afraid we don't understand the request to put explicit examples in the
section on venues for publishing programming systems research; we'd
already listed UIST, VL/HCC, LIVE and PX. If this was about specific
publications instead, we've now referred to some in the footnote on page
3.

@@

The fact of the matter is that almost all of our 22 dimensions are
technical, with the possible exception of Learnability and Sociability
being socio-technical, and some remarks in Integrity vs.~Openness. On
this basis, we strongly disagree with calling the contribution
``socio-technical'' dimensions or similar, as this would give a false
expectation to readers. We appeal to the reviewer to permit us to keep
the name ``technical''---we put a lot of effort into thinking of names
early on, but ``technical dimensions'' was the best out of perhaps only
two viable choices. If this is still unacceptable, we will fall back on
the other name, ``design dimensions'', but if this is still rejected we
would need some help determining an alternative.

>>>>

Section~5 has been reframed as an evaluation of the framework by means
of the two example usages. We've included a summary table for the
dimensional analysis of Dark in section~5.1 and annotated the screenshot
for convenience. We appreciate the reviewer's desire for examples of the
specific interactions. We feel these are best demonstrated through one
of Dark's tutorial videos, so we added a reference to one that addresses
this concern.

@@

Our statement about ``vaguely interesting'' was entirely from
experience, so we relaxed it to something we could more easily support
with references. These can be seen in a footnote with our remarks
linking them to the point we're trying to make. Elsewhere we have
addressed this by deleting the claim (e.g.~for ``holistic view'') or
adding references, for example to the various example systems like Java
and Jupyter. As for explicit examples of venues for publishing
programming systems research: we already listed several examples in
section~2 (UIST, VL/HCC, LIVE, PX) and while further venues could be
listed, we believe these illustrate the range well enough. If this was
about specific publications instead, we've now referred to some in the
footnote on page 3.

@@

Almost all of our 22 dimensions are straightforwardly technical, with
the possible exception of Learnability and Sociability being
socio-technical, and some remarks in Integrity vs.~Openness. Even though
there are some social aspects, we hope to emphasise the technical side.
On this basis, we would rather not call the contribution
``socio-technical'' dimensions or similar, as this would give a false
expectation to readers. Our preferred naming remains ``technical''---we
put a lot of effort into thinking of names early on, but ``technical
dimensions'' was the best out of perhaps only two viable choices. If
this is unacceptable, we could fall back on the other name, ``design
dimensions'', but if that doesn't work we would need some help
determining an alternative.
